Using Incremental Many-to-One Queries to Build a Fast and Tight Heuristic for A* in Road Networks

### 2021-11-15 paper/ch_potentials.tex
consistency uv vs u,v

\todo{$w(uv)$ vs $w(u,v)$, egal welches aber bitte konsistent.}

@@

To obtain a bidirectional stopping criterion, the \emph{average potential} is proposed~\cite{gh-cspas-05}.
It combines a forward and a backward heuristic $\overrightarrow{h}_t$ and $\overleftarrow{h}_s$ into a combined \emph{average heuristic} $h_{\overline{st}}$.
The idea is to use a common reduced graph, whose weights are the average weights of the individual reduced graphs.
Both searches run on the same common reduced graph.
This allows stopping the searches when $\overrightarrow{k} + \overleftarrow{k} \geq \mu$.
Formally, $h_{\overline{st}}(x)$ is defined as $(\overrightarrow{h}_t(x) - \overleftarrow{h}_s(x))/2$.
The forward search uses $h_{\overline{st}}(x)$ as its heuristic.
The backward search uses $-h_{\overline{st}}(x)$.
Unfortunately, average potentials have two downsides.
First, evaluating the average potential requires evaluating both $\overrightarrow{h}_t$ and $\overleftarrow{h}_s$.
Evaluating the average heuristic is therefore slower than evaluating just one of the composing heuristics.
Second, the bidirectional stopping criterion comes at the cost of worse estimates for each direction on its own.
$h_{\overline{st}}(x)$ is a worse estimate for $\dist(x,t)$ than $\overrightarrow{h}_t$.
Similarly, $-h_{\overline{st}}(x)$ is a worse estimate for $\dist(s,x)$ than $\overleftarrow{h}_s$.
The second downside can be partially mitigated through pruning with the composing heuristics.
When the forward search scans an edge $xy$ where $\overrightarrow{D}[x] + w(x,y) + \overrightarrow{h}_s(y) > \mu$ holds, i.e. the distance plus the estimate of the remaining distance is already greater than the currently known tentative distance, it is not necessary to push $y$ into the queue.
The pruning rule for the backward search is analogous.

>>>>

@@

To obtain a bidirectional stopping criterion, the \emph{average potential} is proposed~\cite{gh-cspas-05}.
It combines a forward and a backward heuristic $\overrightarrow{h}_t$ and $\overleftarrow{h}_s$ into a combined \emph{average heuristic} $h_{\overline{st}}$.
The idea is to use a common reduced graph, whose weights are the average weights of the individual reduced graphs.
Both searches run on the same common reduced graph.
This allows stopping the searches when $\overrightarrow{k} + \overleftarrow{k} \geq \mu$.
Formally, $h_{\overline{st}}(x)$ is defined as $(\overrightarrow{h}_t(x) - \overleftarrow{h}_s(x))/2$.
The forward search uses $h_{\overline{st}}(x)$ as its heuristic.
The backward search uses $-h_{\overline{st}}(x)$.
Unfortunately, average potentials have two downsides.
First, evaluating the average potential requires evaluating both $\overrightarrow{h}_t$ and $\overleftarrow{h}_s$.
Evaluating the average heuristic is therefore slower than evaluating just one of the composing heuristics.
Second, the bidirectional stopping criterion comes at the cost of worse estimates for each direction on its own.
$h_{\overline{st}}(x)$ is a worse estimate for $\dist(x,t)$ than $\overrightarrow{h}_t$.
Similarly, $-h_{\overline{st}}(x)$ is a worse estimate for $\dist(s,x)$ than $\overleftarrow{h}_s$.
The second downside can be partially mitigated through pruning with the composing heuristics.
When the forward search scans an edge $xy$ where $\overrightarrow{D}[x] + w(xy) + \overrightarrow{h}_s(y) > \mu$ holds, i.e. the distance plus the estimate of the remaining distance is already greater than the currently known tentative distance, it is not necessary to push $y$ into the queue.
The pruning rule for the backward search is analogous.
